---
title: "Example_Walkthrough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example_Walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction
In this walkthrough, we will go through the various use cases of TangledFeatures and how it outperforms traditional feature selection methods. We will also compare the raw accuracy of the package to other methods including standard black box approaches. 

TangledFeatures relies on the dataset inputted to be correct. If there are categorical features please ensure that it is inputted as a factor. If done correctly, the package will identify the correct correlation based relationships between the variables. 

In this example, we will be using the Boston housing prices data set. There has been some cleaning beforehand so that all the variables are in the correct orientation. 

# Getting Started 
TangledFeatures primarily relies on ggplot2 for visualization, data.table for data manipulation, correlation for various correlation methods and ranger for its Random Forest implementation. There are a few other packages used to run certain features. 

```{r libraries}
options(warn=-1)

library(ranger)
library(igraph)
library(correlation)
library(data.table)
library(fastDummies)
library(ggplot2)

library(randomForest)
library(glmnet)
library(caret)
library(broom)
library(broom.mixed)
library(jtools)   
```

# Loading the Data
To read the data we can use the simple: 

```{r Data Loading}
data <- TangledFeatures::Housing_Prices_dataset
data <- data[,-1]
```

This loads the base Boston housing prices data set. You can load this into the TangledFeatures function by:

```{r Data Cleaning}
Data <- TangledFeatures::DataCleaning(Data = data, Y_var = 'SalePrice')
```

# Correlation and treating the data
We are able to identify the variable class for each variable and assign it's appropriate correlation relationship with other variables. Read more in the Correlation section.

If data_clean is set to 'TRUE' we follow a set of steps to clean the data including cleaning column names, dummy column creation and removal of NAs. Please read more in the 'Data_input' section.

Let's set the function and call it's various outputs 
```{r Function call}
Results <- TangledFeatures::TangledFeatures(Data = TangledFeatures::Housing_Prices_dataset[,-1], Y_var = 'SalePrice', Focus_variables = list(), corr_cutoff = 0.85, RF_coverage = 0.95,  plot = TRUE, fast_calculation = FALSE, cor1 = 'pearson', cor2 = 'polychoric', cor3 = 'spearman')
```

The function returns visualizations and metrics about the correlation as well as other interesting metrics 

```{r Correlation Heatmap}
Heatmap_plot <- Results$Correlation_heatmap
plot(Heatmap_plot)
```

For visualization purposes, we are only working with the top 20 variables. As we can see we can take the various relationships and visualize them on a single graph. TangledFeatures also returns the variables as well as the correlation metric used between them. 


```{r Correlation Graph}
Igraph_plot <- Results$Graph_plot
plot(Igraph_plot)
```

As we can see from the graph, using graph theory algorithms we can trace the interrelationships between the variables. There are two distinct groups that we can see that have about the same effect on the sales price. We can take a single variable from each group as the group representative. 


#here we are going to see the plot summary of this system
```{r Final Variables}
TangledFeatures_variables <- Results$Final_Variables
```

```{r TangledFeatures LM}
formula_TangledFeatures <- as.formula(paste(paste("sale_price", '~'), paste(TangledFeatures_variables, collapse = "+")))
lm_TangledFeatures <- lm(formula_TangledFeatures, data = Data$Cleaned_Data)

summary(lm_TangledFeatures)
```

#Let's see what other feature selection techniques give 

```{r Other feature selection techniques}
library(caret)

control=trainControl(method = "cv",number=5)

set.seed(849)
lasso_caret <- train(x = Data$Cleaned_Data[ , -c("sale_price")], y = Data$Cleaned_Data$sale_price, method = "glmnet",
                trControl=control,preProc = c("center","scale"),
                tuneGrid = expand.grid(alpha = 1,
                                       lambda = 0))

lasso_coef <- coef(lasso_caret$finalModel,lasso_caret$bestTune$lambda)
```

```{r lasso regression}
lasso_coef <- as.data.frame(as.matrix(lasso_coef))
lasso_coef$Var_names <- rownames(lasso_coef) 

lasso_variables <- lasso_coef[which(lasso_coef$s1 > 0),]$Var_names

formula_lasso <- as.formula(paste(paste("sale_price", '~'), paste(lasso_variables[-1], collapse = "+")))
lm_lasso <- lm(formula_lasso, data = Data$Cleaned_Data)

summary(lm_lasso)
```



```{r RFE RandomForest}

control <- rfeControl(functions = rfFuncs, # random forest
                      method = "repeatedcv", # repeated cv
                      repeats = 2, # number of repeats
                      number = 2) # number of folds


result_rfe <- rfe(x = Data$Cleaned_Data[ , -c("sale_price")], 
                   y = Data$Cleaned_Data$sale_price, 
                   sizes = c(1:40),
                   rfeControl = control)
result_rfe <- predictors(result_rfe)
```

#Running an lm model on this data
```{r RFE lm}
formula_rfe <- as.formula(paste(paste("sale_price", '~'), paste(result_rfe, collapse = "+")))
lm_rfe <- lm(formula_rfe, data = Data$Cleaned_Data)

summary(lm_rfe)
```
```{r Plotting and Comparing Coefficents}
plot_summs(lm_rfe, lm_lasso, lm_TangledFeatures, coefs = names(lm_TangledFeatures$coef)[-c(1:2, 8)], 
            omit.coefs = c("bsmt_qual_ex"),
            model.names = c("Random Forest RFE", "Lasso", "TangledFeatures"))
```

If we take a look at the coefficent behavior across three models for a few variables, we can see that it is largely the same with one major exception. Both Lasso and RandomForest make the garage_area variable negative, as it is highly correlated with other variables. TangledFeatures takes the variable interrelationships into account and generates the correct variable effect. 

